Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-06-05 PaperLatex/paper.tex
Rewrite main body
Fix citation style

"xolotl" handles this problem through symbolic manipulation of "C++" objects in "MATLAB". Built from the ground up in "C++", "xolotl" maintains all the advantages of custom compiled code, but can run in "MATLAB" without the user having to touch the "C++" code. "xolotl" represents compartment, conductance, synapse, and controllers as "cpplab" objects, which map to underlying "C++" header files. In this way, properties of the "xolotl" network can be examined and changed using object-oriented paradigms. The object specifies the "integrate" function, not the other way around.

@@

SG-S designed and implemented the core of the "xolotl" toolbox. AH contributed to the code base, created the online user documentation, and wrote the manuscript. EM supervised the project. All authors reviewed the paper.

@@

\section*{Acknowledgments}
The authors would like to thank Mara CP Rue and Hillary Rodgers for beta-testing the "xolotl" software. Janis Li helped to prepare some conductance header files.

>>>>

"xolotl" handles this problem through symbolic manipulation of "C++" objects in "MATLAB". Built from the ground up in "C++", "xolotl" maintains all the advantages of custom compiled code, but can run in "MATLAB" without the user having to touch the "C++" code. "xolotl" represents compartment, conductance, synapse, and controllers as "cpplab" objects, which template from underlying "C++" header files. In this way, properties of the "xolotl" network can be examined and changed using object-oriented paradigms. The object specifies the "integrate" function, not the other way around.

@@

SG-S designed and implemented the core of the "xolotl" toolbox. AH contributed to the code base, created the online user documentation. SG-S and AH wrote the manuscript. EM supervised the project. All authors reviewed the paper.

@@

\section*{Acknowledgments}
The authors would like to thank Mara CP Rue and Hillary Rodgers for beta-testing the "xolotl" software. Janis Li helped to prepare many conductance header files.
